Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-21 NEUROC/sec4-experiments.tex
更新sample实验的描述。

In the implementation in PyG, the GNN model and the dataset resided on the GPU side.
%
To process each epoch, PyG sampled the original dataset in the main memory and generated several batches.
%
Each batch was a small subgraph of the dataset.
%
To train on each batch, PyG sent the sampled subgraph to the GPU, calculated the gradients on the subgraph, and updated the model parameters directly on the GPU.
%
With the sampling techniques, the model parameters were updated by a stochastic gradient descent optimizer.
%
PyG conducted the evaluation phase every several epochs or batches (either on the CPU side or the GPU side) to determine whether to stop the training.
%
In this section, the experiments focused on the training phase of each batch.

\figurename~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the sampled subgraph changed with the batch size.
%
For the neighbor sampler, the relative batch size was the proportion of the sampled vertices of the last GNN layer in $\mathcal{V}$.
%
For the cluster sampler, the relative batch size was the proportion of the sampled partitions in all partitions of the graph.
%
The neighbor sampler was very sensitive to the batch size.
%
As the batch size increased, the size of the sampled subgraph first increased quickly and then stabilized.
%
The cluster sampler was much less sensitive compared to the neighbor sampler.
%
The number of vertices and the average degree of the sampled subgraphs increased linearly with the batch size.

@@

The disadvantage of the sampling technique was wasting GPU resources.
%
As the sampling techniques were only effective under small batch sizes, the sampled subgraphs were very small in those cases.
%
They could not make full use of the computing power of a GPU.
%
To simulate the situation, we generated random graphs with few vertices and measured the training time per batch in \figurename~\ref{fig:exp_small_graph_train_time}.
%
As the number of vertices increased, the training time was almost unchanged except for GaAN.
%
The training time of GaAN increased only with $|\mathcal{V}| \geq 4000$.

>>>>

In the implementation in PyG, the GNN model resided on the GPU side and the dataset resided on the host side.
%
To process each epoch, PyG sampled the original dataset in the main memory and generated several batches.
%
Each batch was a small subgraph of the dataset.
%
To train the GNN model with each batch, PyG sent the sampled subgraph to the GPU, calculated the gradients on the subgraph, and updated the model parameters directly on the GPU.
%
With the sampling techniques, the model parameters were updated by a stochastic gradient descent optimizer.
%
PyG conducted the evaluation phase every several epochs or batches (either on the CPU side or the GPU side) to determine whether to stop the training.
%
In this section, the experiments focused on the training phase of each batch.

\figurename~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the sampled subgraph changed with the batch size.
%
For the neighbor sampler, the relative batch size was defined as the proportion of the sampled vertices of the last GNN layer in $\mathcal{V}$.
%
For the cluster sampler, the relative batch size was defined as the proportion of the sampled partitions in all partitions of the graph.
%
The experimental results indicated that the neighbor sampler was very sensitive to the batch size.
%
As the batch size increased, the size of the sampled subgraph first increased quickly and then stabilized.
%
The cluster sampler was much less sensitive compared to the neighbor sampler.
%
The number of vertices and the average degree of the sampled subgraphs increased linearly with the batch size.

@@

The disadvantage of the sampling technique was wasting GPU resources.
%
As the sampling techniques were only effective under small batch sizes, the sampled subgraphs were very small in those cases.
%
They could not make full use of the computing power of a GPU.
%
To simulate the situation, we generated random graphs with few vertices and measured their training time per epoch in \figurename~\ref{fig:exp_small_graph_train_time}.
%
As the number of vertices increased, the training time was almost unchanged except for GaAN.
%
The training time of GaAN increased only when $|\mathcal{V}| \geq 4000$.
